\phantomsection\addcontentsline{toc}{chapter}{Acknowledgments}
\chapter*{Acknowledgments}
\markboth{Acknowledgments}{Acknowledgments}

In the final stages of my thesis I would like to thank many people for their support during the years.

\begin{itemize}

\item{} First, I would like to express my gratitude towards Prof. Dr. Achim Stahl for giving me the opportunity to work at this complex topic in such an immense collaboration. Especially, I am thankful for the possibility to spend one year at CERN and for letting me travel to the CMS Meeting in Taipei.

\item{} I also like to thank Prof. Dr. Stefan Schael for reviewing this thesis as second referee.

\item{} Through the years I received supervision from PD Dr. Oliver Pooth. Thanks for your helpful work and also for the conversations at the patio of the restaurant at CERN.

\item{} Next, I would like to thank the whole CMS working group of the Institute 3B for the friendly atmosphere. Especially, all those who did the hard work of proof-reading this thesis. Without the help of Yusuf Erdogan, Heiko Geenen, Bastian Kargoll, Alexander Nehrkorn, Ian Nugent and Oliver Pooth this work would not be in the good shape it is.

\item{} At a usual day in office there have always been two points in time where work was put in background. Thanks to all who contributed to the 11am coffee (and cake) breaks and to the pleasurable table-soccer matches. Expanding this a bit I like to thank the whole team of the Institute 3B. There has always been a nice and friendly environment during all the years.

\item{} In such a big collaboration it is hard to pick a few people who helped me. Very important for this work were Giuseppe Cerati, Giacomo Sguazzoni, Kevin Stenson and Andrea Venturi. They all contributed their ideas to my work and created a very nice spirit in convening the Tracking group of CMS.


\selectlanguage{german}

\item{} Abschlie\ss{}end m\"o{}chte ich meine Dankbarkeit gegen\"u{}ber meiner Familie und meinen Freunden zum Ausdruck bringen. Von Beginn an bis jetzt war ihre Betreuung immer sp\"u{}rbar und half bei so manchen (unphysikalischen) Problemen.

\selectlanguage{english}

\end{itemize}